---
title: "Education Inequality"
author: "Hannah Barrow"
date: "`r Sys.Date()`"
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(flexdashboard)
library(ggplot2)
library(dplyr)
library(knitr)
```
################################################################################
# About

## Right Column

### 

```{r, echo=FALSE}
valueBox("SGD's of Interest:")
```

### 

**[#4: Quality Education](https://sdgs.un.org/goals/goal4)** "Ensure inclusive and equitable quality education and promote lifelong learning opportunities for all" 

**[#5: Gender Equality](https://sdgs.un.org/goals/goal5)** "Achieve gender equality and empower all women and girls"

For this data story, I want to explore the differences in education quality among countries with different economic levels and practices. I also want to explore gender inequalities in education. 

################################################################################
# The Data

I pulled my data sets from [Our World In Data](https://ourworldindata.org). 

[Government spending on education](https://ourworldindata.org/grapher/education-spending)

```{r, eval=TRUE, echo=FALSE, message=FALSE}
library(readr)
library(dplyr)

url <- 'https://ourworldindata.org/grapher/education-spending.csv?v=1&csvType=full&useColumnShortNames=true&spending_type=gdp_share&level=all'

edu_spending_origional <- read_csv(url)

edu_spending <- edu_spending_origional %>% 
  rename(spending_gdp = government_expenditure_on_education_as_a_percentage_of_gdp__pct__xgdp_fsgov)

edu_spending %>% head
```

[Gender gap in primary, secondary and tertiary education](https://ourworldindata.org/grapher/gender-gap-education-levels)

```{r, eval=TRUE, echo=FALSE, message=FALSE}
library(readr)
library(dplyr)

url <- 'https://ourworldindata.org/grapher/gender-gap-education-levels.csv?v=1&csvType=full&useColumnShortNames=true'

edu_gender_origional <- read_csv(url)

edu_gender <- edu_gender_origional %>% 
  rename(f_tertiary = f_tertiary_enrollment_rates_combined_wb,
         m_tertiary = m_tertiary_enrollment_rates_combined_wb,
         f_primary = f_primary_enrollment_rates_combined_wb,
         m_primary = m_primary_enrollment_rates_combined_wb,
         m_lower_secondary = total_net_enrolment_rate__lower_secondary__male__pct,
         f_lower_secondary = total_net_enrolment_rate__lower_secondary__female__pct,
         m_upper_secondary = total_net_enrolment_rate__upper_secondary__male__pct,
         f_upper_secondary = total_net_enrolment_rate__upper_secondary__female__pct)

edu_gender %>% head
```

[Inequality in education](https://ourworldindata.org/grapher/inequality-in-education)

```{r, eval=TRUE, echo=FALSE, message=FALSE}
library(readr)
library(dplyr)

url <- 'https://ourworldindata.org/grapher/inequality-in-education.csv?v=1&csvType=full&useColumnShortNames=true'

edu_equality <- read_csv(url)

edu_equality %>% head
```

################################################################################
# Sources

1. [Children from the poorest households benefit the least from national public education funding](https://www.unicef.org/eca/press-releases/children-poorest-households-benefit-least-national-public-education-funding-unicef)

2. [Closing the Gap: Girls' Education and Women's Labor](https://blogs.worldbank.org/en/education/closing-gap-tackling-remaining-disparities-girls-education-and-womens-labor-market)

3. [Investing in Quality Education for Economic Development, Peace, and Stability](https://www.csis.org/analysis/investing-quality-education-economic-development-peace-and-stability)

4. [More young women than men have college degrees](https://www.pewresearch.org/short-reads/2024/11/18/us-women-are-outpacing-men-in-college-completion-including-in-every-major-racial-and-ethnic-group/)

5. [New UNESCO Report shows extent of global inequalities in education and calls for greater inclusion as schools re-open](https://www.unesco.org/en/articles/new-unesco-report-shows-extent-global-inequalities-education-and-calls-greater-inclusion-schools-re)



################################################################################
################################################################################
# Key Results

## Left column

### Left top row

```{r}
plot(cars)
```

### Left bottom row

```{r}
head(iris) %>% kable
```

## Right column

### Top right row

```{r, echo=FALSE}
valueBox("whatever text i want!")
```

### Bottom rigth row

Some **nice words** to read. 

# Fancier results

## Left column

### Tab 1

```{r}
plot(cars)
```

> Caption would go here

### Tab 2

```{r}
iris %>% kable
```

## Rigth column {data-width = 350}

### Text take-away

```{r, echo = FALSE}
valueBox("33%", icon = "fa-brands fa-firefox")
```

### Really really low

```{r}
gauge(19,
      min = 0, max = 50,
      gaugeSectors(
        success = c(41, 50),
        warning = c(21, 40),
        danger = c(0, 20)
      ))
```

### Fourth box

Even more content can go here:
plot, table, widget, or just a narrative / explanation. 

# Details {data-icon = "fa-table"}

By the way, here are other [cool icons](https://fontawesome.com). 
Some aren't free. 

This tab provides wide rows rather than split-screen columns. 

### Row 1

```{r}
iris %>% kable
```

### Row 2

# Map

```{r, echo = FALSE}
library(leaflet)

#different flavors of maps

#leaflet() %>% 
#  addTiles() %>% 

#leaflet() %>% 
#  addProviderTiles(providers$Esri.WorldImagery)

#leaflet() %>% 
#  addProviderTiles(providers$Esri.WorldTopoMap)

#sewanee <- data.frame(longitude = -85.9211,
#                      latitude = 35.2031)
#leaflet() %>% 
#  addTiles() %>% 
#  addCircleMarkers(data = sewanee,
#             color = "purple",
#             radius = 30,
#             popup = "Heyyyyyy!")

url <- "https://docs.google.com/spreadsheets/d/18OA2UP-9oDE7hGkfEjBHhV36Z70p2pQ7I6_N-Ie8KtM/edit?usp=sharing"

library(gsheet)
locs <- gsheet2tbl(url)
locs

leaflet() %>% 
  addTiles() %>% 
  addCircleMarkers(data = locs,
             color = locs$marker_color,
             radius = locs$marker_size,
             popup = paste0(locs$location,
                            "<br/>",
                            locs$description))
```

